% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{org_cv}
\usepackage{marvosym}
\usepackage{accsupp}
\date{2022-06-06}
\title{Edwin Hu}
\hypersetup{
 pdfauthor={Edwin Hu},
 pdftitle={Edwin Hu},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\newcommand\hiddentext[2]{%
    \BeginAccSupp{ActualText={\detokenize{#1}}}%
      #2
    \EndAccSupp{}%
}

\begin{center}
\begin{tabular}{ll}
NYU School of Law & Last Updated: 2022-06-06\\
\href{https://www.law.nyu.edu/centers/icgf}{Institute for Corporate Governance \& Finance} & \Letter: \texttt{edwin.hu@nyu.edu}\\
40 Washington Sq. South & \Mundus: \href{http://edwinhu.github.io}{edwinhu.github.io}\\
New York, NY 10012 & \\
\end{tabular}
\end{center}

\section*{Employment}
\label{sec:orgb3b58ff}
\subsection*{\textbf{2020--Present: Research Fellow}}
\label{sec:org90c2d1e}
NYU School of Law, New York, NY\\
\href{https://www.law.nyu.edu/centers/icgf}{Institute for Corporate Governance \& Finance}

\begin{itemize}
\item Research in investor protection, corporate governance, and financial markets.
\end{itemize}

\subsection*{\textbf{2018--2020: Counsel to \href{https://www.sec.gov/biography/commissioner-robert-j-jackson}{Commissioner Robert J. Jackson Jr.}}}
\label{sec:org5f3d328}
Securities and Exchange Commission, Washington, D.C.

\begin{itemize}
\item Chief economic advisor on all SEC policy issues.
\end{itemize}

\subsection*{\textbf{2016--2018: Financial Economist Fellow}}
\label{sec:org4607ad6}
Securities and Exchange Commission, Washington, D.C. \\
\href{http://www.sec.gov/dera}{Division of Economic and Risk Analysis}

\begin{itemize}
\item Economic analysis of controversial issues in financial markets.
\end{itemize}

\section*{Education}
\label{sec:orgcee1e84}
\subsection*{\textbf{2020--2023 (Expected): \href{https://www.law.nyu.edu}{NYU School of Law}}}
\label{sec:orgf8a699f}
\begin{itemize}
\item J.D., \href{https://www.law.nyu.edu/furmanprogram}{Furman Scholar}.
\end{itemize}

\subsection*{\textbf{2010--2016: \href{http://business.rice.edu}{Rice University}}}
\label{sec:org8eb9a5d}
\begin{itemize}
\item Ph.D., M.A. \href{http://business.rice.edu/PhD\_Finance\_Area.aspx}{Finance}.
\end{itemize}

\subsection*{\textbf{2006--2010: \href{http://www.washington.edu}{University of Washington}} \emph{Cum Laude}}
\label{sec:orgf8f1984}
\begin{itemize}
\item B.S.  \href{http://econ.washington.edu/}{Economics}, \href{https://www.math.washington.edu/acms/}{Applied and Computational Mathematical Sciences}.
\end{itemize}

\section*{Selected Policy Work}
\label{sec:orgaf86523}
\subsection*{\href{https://www.sec.gov/news/speech/speech-jackson-061118}{Stock Buybacks and Corporate Cashouts}}
\label{sec:org8ca986f}
\begin{itemize}
\item Conducted research showing that the market reacts negatively to
insider selling after stock buyback announcements.
\item Cited in Biden White House Budget Proposal (\href{https://www.nytimes.com/2022/03/28/business/dealbook/biden-stock-buybacks.html}{New York Times}).
\end{itemize}
\subsection*{Lisa D. Cook Federal Reserve Confirmation Team}
\label{sec:orgafcbc8b}
\begin{itemize}
\item Prepared Professor Cook for her historic Senate Confirmation Hearing.
\end{itemize}
\subsection*{2020 Biden Policy Committee}
\label{sec:org590805d}
\begin{itemize}
\item Financial Markets and Corporate Governance Working Group.
\end{itemize}
\subsection*{\href{https://www.sec.gov/news/public-statement/statement-jackson-060519-iabd}{Rules Governing Investment Advice} (Regulation Best Interest)}
\label{sec:org560a7f1}
\begin{itemize}
\item Conducted research showing that the proposed interpretation of the
fiduciary standard was related to higher rates of conflicted advice.
\item Cited by Senators Warren, Booker, Speaker Pelosi, Chair Waters.
\end{itemize}
\end{document}
